### 2012-02-11 trunk/GUIErrorDetector/paper/evaluation.tex
address the comments by jamie

We first inspected the source code of each subject to determine whether any
native methods or project-specific GUI interaction patterns were implemented.
Only SGTPuzzler uses native methods to interact with
the underlying operating system. For it, we manually checked the possible
Java methods that a native method may call, and then added \annotationnum \CodeIn{@CalledByNativeMethods}
annotations for it. Two subjects MyTracks and Fennec employ a customized pattern
to interact with the GUI framework. For example, in MyTracks, all non-UI
threads are initialized via using the library method \CodeIn{android.os.} \CodeIn{handler.handleCallback}.
% the \CodeIn{safeInvokeXX}
%method in the XXX subject first checks whether the current thread is the UI-thread, and
%then determines whether to direct access a GUI object or wrap the code with
%message passing. 
We added \filternum user-defined filters for these two subjects.
%to indicate
%that they are safe to be invoked from any thread. 
In this experiment, none of the paper
authors was familiar with the subjects; but we found it is quite easy
to add extra annotations and user-defined filters. All these
manual parts took less than a total of 60 minutes.

@@

As shown Table~\ref{table:results},  our tool found
real errors in each subject program. Using the 1-CFA
call graph algorithm, our tool issued 22 warnings, among
which \bugs warnings reveal \bugs distinct errors (\newbugs were previously unknown),
2 warnings are false positives, and the remaining 8 warnings
are redundant. Section~\ref{sec:reflectionaware} compares with other call graph
construction algorithms.

@@

414.public void refresh() \ttlcb
415.  getViewer().refresh();
416.\ttrcb
\end{alltt}
\end{CodeOut}
\smallstep
\vspace*{-2.0ex} \Caption{{\label{fig:pluginerror} An
invalid thread access error reported by our tool
for the EclipseRunner plugin. In Eclipse, the
callback method \CodeIn{resourceChanged} on line 181
is invoked by non-UI threads when a \CodeIn{ResourceChangeEvent}
happens. However, the \CodeIn{refresh} method directly accesses
GUI objects (to refresh the view on line 415) without any
protection and thus triggers the error.
This error has been reported by other users 13 months after the
buggy code was checked in, and fixed by developers.
}} %\vspace{-5mm}
\end{figure}

@@

\noindent \textbf{\textit{Summary.}} Although a static analysis may
issue false positives or redundant reports, a set of well-designed
error filters can remove most of them.
%Heuristic filter, effective.

>>>>

We first inspected the source code of each subject to determine whether any
native methods or project-specific GUI interaction patterns were implemented.
Only SGTPuzzler uses native methods to interact with
the underlying operating system. For it, we manually checked the possible
Java methods that a native method may call, and then added \annotationnum \CodeIn{@CalledByNativeMethods}
annotations for it. Two subjects, MyTracks and Fennec, employ a customized pattern
to interact with the GUI framework. For example, in MyTracks, all non-UI
threads are initialized via using the library method \CodeIn{android.os.} \CodeIn{handler.handleCallback}.
% the \CodeIn{safeInvokeXX}
%method in the XXX subject first checks whether the current thread is the UI-thread, and
%then determines whether to direct access a GUI object or wrap the code with
%message passing. 
We added \filternum user-defined filters for these two subjects.
%to indicate
%that they are safe to be invoked from any thread. 
In this experiment, none of the paper
authors was familiar with the subjects, but we found it was quite easy
to add extra annotations and user-defined filters. All these
manual parts took less than a total of 60 minutes.

@@

As shown in Table~\ref{table:results},  our tool found
real errors in each subject program. Using the 1-CFA
call graph algorithm, our tool issued 22 warnings, among
which \bugs warnings reveal \bugs distinct errors (\newbugs were previously unknown),
2 warnings are false positives, and the remaining 8 warnings
are redundant. Section~\ref{sec:reflectionaware} compares with other call graph
construction algorithms.

@@

414.public void refresh() \ttlcb
415.  getViewer().refresh();
416.\ttrcb
\end{alltt}
\end{CodeOut}
\smallstep
\vspace*{-2.0ex} \Caption{{\label{fig:pluginerror} An
invalid thread access error reported by our tool
for the EclipseRunner plugin. In Eclipse, the
callback method \CodeIn{resourceChanged} on line 181
is invoked by non-UI threads when a \CodeIn{ResourceChangeEvent}
happens. However, the \CodeIn{refresh} method directly accesses
GUI objects (to refresh the view on line 415) without any
protection and thus triggers the error.
This error was reported by other users 13 months after the
buggy code was checked in, and fixed by developers.
}} %\vspace{-5mm}
\end{figure}

@@

\noindent \textbf{\textit{Summary.}} Our proposed error filters are 
effective in reducing the number of warnings.
%Although a static analysis may
%issue false positives or redundant reports, a set of well-designed
%error filters can remove most of them.
%Heuristic filter, effective.
